\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-21 doc/incertae_sedis.tex
Added clarifying comments on the alternative semantics.

\subsubsection{A semantics that disallows inter-digitating
\emph{incertae sedis} siblings}

@@

\subsubsection{An alternative semantics that allows inter-digitating
incertae sedis siblings}

@@

>>>>

\subsubsection{semantics \#1a: The original, simplest semantics}
\begin{align}
    \mathcal{E}(n) & = \mathcal{E}(parent(n))\cup\left[\mathcal{I}(s)\big|s\in
           siblings(n), s \text{ not \emph{incertae sedis}}\right].\label{eq:exclude-set-formula-1a}
\end{align}
This semantics \emph{does} allow interdigitation.

\subsubsection{semantics \#1b: modified to disallow inter-digitating
\emph{incertae sedis} siblings}

@@

\subsubsection{An alternative semantics that allows placing an incertae sedis group within an incertae-sedis great-uncle}

\bdrcomment{This semantics is actually designed to allow the situation in Figure \ref{fig:Placing-one-incertae}.

  The problem is (might be) as follows: if we have the tree ``((?A1,A2)A,((D)C)B)MRCA;'', where A1 is incertae sedis, then we can place A1 within D.  This semantics does not exclude A1 from B, C, or D.  So, if A is broken, then nothing prohibits A1 from intruding into B, C, D, etc.

  The purpose of this was to allow placing B as a siblign to A1 and then placing A1 within B -- \emph{if} B were incertae sedis.  But B is not incertae sedis.

  We could try to fix up this situation by adding cases to the exclude rules to say that B excludes A1 if B is not incertae sedis.  But adding cases makes things messier.  I think it also does not actually solve the problem: suppose we mark B incertae sedis, but do NOT place it as sibling to A1.  Then again if A is broken, A1 can intrude into B.  We really want to allow A1 into B only if B is placed as sibling to A1, and I'm not sure how to do that with the partial-split-based semantics.  If you see a way, then great!
}

@@

\bdrcomment{I didn't really finish working this one out.}
